%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author : Samuel Marton, Tomas Polasek (template)
% Description : First exercise in the Introduction to Game Development course.
%   It deals with an analysis of a selected title from the point of its genre, 
%   style, and mechanics.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,english]{article}

\usepackage[left=2.50cm,right=2.50cm,top=1.50cm,bottom=2.50cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\newcommand{\ph}[1]{\textit{[#1]}}

\title{%
Analysis of Mechanics%
}
\author{%
Samuel Marton (xmarto03)%
}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

{%
\large

\begin{itemize}

\item[] \textbf{Title:} \textit{Cry of fear}

\item[] \textbf{Released:} \textit{2012 as a half-life mod, 2013 standalone}

\item[] \textbf{Author:} \textit{Team Psykskallar}

\item[] \textbf{Primary Genre:} \textit{Survival horror}

\item[] \textbf{Secondary Genre:} \textit{First person shooter}

\item[] \textbf{Style:} \textit{Gritty, Uncanny}

\end{itemize}

}

\section*{\centering Analysis}

\subsection*{What is cry of fear?}

Cry of fear is a survival horror game initially released as a mod for Half-life and later as a standalone game. We play as Simon who wakes up in a dark alley in Sweden and is trying to find his way home. Along the way he meets a plethora of scary enemies that he needs to kill to progress. 

\subsection*{Genres}

In a survival horror game you must manage your resources to survive. In this game it's your health, which can be replenished using syringes, and you can lose it when fighting enemies. Another valuable resource is ammo. Most enemies can be defeated with a knife but there is a bigger chance of losing health when doing so. Player often makes the decision whether to kill an enemy with a knife or a gun based on which of these resources they have more of.

This game is also a first person shooter. There are several guns you get to use in this game: a semi-automatic pistol, a burst fire pistol, a pump shotgun, a bolt action sniper rifle, and an assault rifle. However guns are often used only as a last resort. There are only a few types of enemies that require them to be defeated.

\subsubsection*{How do they work together?}

Survival horror and first person shooter work together very well. Some examples are Resident Evil, Alien: Isolation, In Sound Mind and of course, Cry of Fear. The FPS aspect of the game naturally adds an extra resource, ammunition, for the player to worry about.

\subsection*{Style}

The game uses GoldSrc engine to achieve a style similar to Half-life 1, but much more darker. The simple graphics limited by the engine enhance the horror aspect of the game. Models of the enemies are the definition of uncanny valley, with twitchy and unsettling animations. 




\end{document}
